Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-03-20 draft.tex
add new section--Stop the Bully

Thus, we propose the hybrid placement as a reconcile solution. In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation. We evaluate the performance of hybrid placement\&routing configurations with parallel Workload \Rmnum{1}. AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocation.

Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing, together with other configurations. As we see from Figure \ref{fig:hyb-plcmt-amg-commtime},

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:hyb-plcmt-amg-commtime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
        \caption{MG Communication Time}
        \label{fig:hyb-plcmt-mg-commtime}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
        \caption{CR Communication Time}
        \label{fig:hyb-plcmt-cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement\& routing configurations. }
   \label{fig:hyb-plcmt-apps-commtime}
\end{figure*}

@@

 \vspace{5\baselineskip}

>>>>

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:hyb-plcmt-amg-commtime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
        \caption{MG Communication Time}
        \label{fig:hyb-plcmt-mg-commtime}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
        \caption{CR Communication Time}
        \label{fig:hyb-plcmt-cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement\& routing configurations. \textbf{HM, HA, HPA} denote hybrid placement coupled with minimal, adaptive and progressive adaptive routing respectively. }
   \label{fig:hyb-plcmt-apps-commtime}
\end{figure*}

Thus, we propose the hybrid placement as a reconcile solution. In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation. We evaluate the performance of hybrid placement\&routing configurations with parallel Workload \Rmnum{1}. AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocation. Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing schemes, together with other configurations.

MultiGrid and CrystalRouter have basically the same performance with hybrid placement compared against random placement. Since they get random allocation in the hybrid placement scheme. AMG being improved a lot when hybrid placement in use. Compared with ``RA" and ``RPA", ``HA" and ``HPA" can significantly reduce AMG communication time, shown in Figure \ref{fig:hyb-plcmt-amg-commtime}. This is due the contiguous allocation AMG gets in the hybrid placement scheme. AMG doesn't share router with other applications. However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter is still being redirected to the groups where AMG resides. Since AMG is less communication-intensive and can not fully utilize network bandwidth, it is likely that the intermediate routers pick for the traffic from MultiGrid and CrystalRouter are from AMG's group.

@@

 \vspace{1\baselineskip}
